Time slice analyses

### 2017-11-24 analyses/02-time-slice-analyses.Rmd
updated function/arguments names for 0.4.2

> TG: for the following pipeline, I've reduced the number of rarefaction that highly increased the calculation time.
We now only calculate the disparity for the non-rarefied subsamples and the subsamples rarefied to contain only 3 taxa (the lowest level of rarefaction).
We can use the full rarefaction if we want to plot rarefaction curves later on.

@@

```{r, fig.width = 12, fig.height = 18}
## Set the list of available models
models <- list("equalbins", "acctran", "deltran", "punctuated", "gradual")

@@

## Adding the legend
legend(x = "bottomleft", legend = c("time bins", "acctran", "deltran", "punctuated", "gradual"),
  col = colors[1:5], lty = 1, bg = "white")

>>>>

> TG: for the following pipeline, I've reduced the number of rarefaction that highly increased the calculation time.
We now only calculate the disparity for the non-rarefied subsets and the subsets rarefied to contain only 3 taxa (the lowest level of rarefaction).
We can use the full rarefaction if we want to plot rarefaction curves later on.

@@

```{r, fig.width = 12, fig.height = 18}
## Set the list of available models
models <- list("equalbins", "acctran", "deltran", "random", "proximity")

@@

## Adding the legend
legend(x = "bottomleft", legend = c("time bins", "acctran", "deltran", "random", "proximity"),
  col = colors[1:5], lty = 1, bg = "white")
